Generalization Errors of Hard Parameter Sharing: High-dimensional Asymptotics and Implications

### 2020-09-20 arxiv/diff_cov.tex
wip

\section{The Different Covariates Setting}
As mentioned in Section \ref{sec_prelim}, the optimization objective \eqref{eq_mtl} is non-convex in general.
Therefore, we consider an arbitrary local minimum $B, W_1, W_2$, in particular when $B = \hat{B}(W_1, W_2)$ satisfies the local optimality condition.
We derive deterministic conditions to compare the prediction loss of the local minimum to single-task learning.

@@

	In the above equation, $a_1$ and $a_2$ are the solutions of the following two equations that only depend on the sample sizes $\rho_1, \rho_2$, and the singluar values of the covariate shift matrix $M$:
	\begin{align}
		a_1 + a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad a_1 + \frac1{\rho_1 + \rho_2}\cdot \bigbrace{\frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} = \frac{\rho_1}{\rho_1 + \rho_2}. \label{eq_a12extra}
	\end{align}
\end{definition}
%We now state our main result for two tasks with both covariate and model shift. It shows that the information transfer is determined by two deterministic quantities $\Delta_{\bias}$ and $\Delta_{\vari}$, which give the change of model shift bias and the change of variance, respectively. The exact forms of $\Delta_{\bias}$ and $\Delta_{\vari}$ will be given in Lemma \ref{thm_model_shift}.

>>>>

\section{The Different Covariates Setting}

As mentioned in Section \ref{sec_prelim}, the optimization objective \eqref{eq_mtl} is non-convex in general.
Therefore, we consider an arbitrary local minimum and provide generalization bounds that scale with key properties of task data such as sample sizes and covariate shifts.
We focus on the two-task case to better understand the impact of having different sample sizes and different covariates in hard parameter sharing. %We derive deterministic conditions to compare the prediction loss of the local minimum to single-task learning.

We first provide a key technical tool that we derived using recent developments in random matrix theory \cite{??}.
To motivate our study, we consider a specialized setting where the output layer weights $A_1, A_2$ are both equal to one.
Without loss of generality, we consider task two.
For this setting, we can obtain the hard parameter sharing estimator $\hat{\beta}_2^{\MTL} = B A_2 = B$ by solving $B$ in equation \eqref{eq_mtl} as follows:
\begin{align*}
	\hat{\beta}_2^{\MTL} = {\hat{\Sigma}}^{-1} ({X^{(1)}}^{\top} Y^{(1)} + {X^{(2)}}^{\top} Y^{(2)}), \text{ where } \hat{\Sigma} = {X^{(1)}}^{\top} X^{(1)} + {X^{(2)}}^{\top} X^{(2)}
\end{align*}
Next, we derive the prediction loss of hard parameter sharing in expectation over the random noise, since the empirical quantity is close to the expectation similar to what we have shown in Claim \ref{claim_pred_err}:
\begin{align*}
	\exarg{\cE}{L(\hat{\beta}_2^{\MTL}) \mid X^{(1)}, X^{(2)}} =
	\bignorm{(\Sigma^{(2)})^{1/2} \hat{\Sigma}^{-1} {X^{(1)}}^{\top} X^{(1)} (\beta^{(1)} - \beta^{(2)})}^2
	+ \sigma^2 \bigtr{\Sigma^{(2)}\hat{\Sigma}^{-1}}.
\end{align*}

@@

	In the above equation, $a_1$ and $a_2$ are the solutions of the following two equations that only depend on the sample sizes $\rho_1, \rho_2$, and the singular values of the covariate shift matrix $M$:
	\begin{align}
		a_1 + a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad a_1 + \frac1{\rho_1 + \rho_2}\cdot \bigbrace{\frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} = \frac{\rho_1}{\rho_1 + \rho_2}. \label{eq_a12extra}
	\end{align}
\end{definition}
%We now state our main result for two tasks with both covariate and model shift. It shows that the information transfer is determined by two deterministic quantities $\Delta_{\bias}$ and $\Delta_{\vari}$, which give the change of model shift bias and the change of variance, respectively. The exact forms of $\Delta_{\bias}$ and $\Delta_{\vari}$ will be given in Lemma \ref{thm_model_shift}.
